Converging High-Throughput and High-Performance Computing Paradigms: \\ A Case Study of Using Abstractions to Bridge the Divide

### 2017-03-12 PandaOverview.tex
Clean up
scattered changes.

\begin{itemize}
  \item No MPI tasks?
  \item Pilot multitenancy?
  \item PanDA Server Brokerage component and Event service interaction?
  \item PanDA Server Data Service component and Event Service interaction?
\end{itemize}

@@

\paragraph{\textbf{AutoPyFactory}} this subsystem implements a factory to submit
pilots locally and to both grid and cloud
sites~\cite{caballero2012autopyfactory}. Implemented to be executed as a single
demonized process, AutoPyFactory enables the concurrent spawning of multiple job
submission processes called APFQueue. Each APFQueue can communicate with PanDA
Server and the Brokerage module to collect information about the state of the
jobs it manages and, on the base of this information, submit new pilots to one
site per APFQueue. AutoPyFactory implements functionalities to evaluate the
number of pilots already instantiated on each site, and to apply a consistent
and adequate pressure on their batch queues. Submission is performed via the
Condor-G batch system~\cite{frey2002condor}, enabling submission to multiple
type of sites. AutoPyFactory exposes a dedicated monitoring service, feeding
information to the PanDA Monitoring subsystem. A proxy manager is also run,
enabling certificate-based authentication and authorization.

>>>>

% \begin{itemize}
%   \item No MPI tasks?
%   \item Pilot multitenancy?
%   \item PanDA Server Brokerage component and Event service interaction?
%   \item PanDA Server Data Service component and Event Service interaction?
% \end{itemize}

@@

\paragraph{\textbf{AutoPyFactory}} this subsystem implements a factory to submit
pilots locally and to both grid and cloud
sites~\cite{caballero2012autopyfactory}. Implemented to be executed as a single
demonized process, AutoPyFactory enables the concurrent spawning of multiple job
submission processes called APFQueue. Each APFQueue can communicate with PanDA
Server and the Brokerage module to collect information about the state of the
jobs it manages and, on the basis of this information, submit new pilots to one
site per APFQueue. AutoPyFactory implements functionalities to evaluate the
number of pilots already instantiated on each site, and to apply a consistent
and adequate pressure on their batch queues. Submission is performed via the
Condor-G batch system~\cite{frey2002condor}, enabling submission to multiple
type of sites. AutoPyFactory exposes a dedicated monitoring service, feeding
information to the PanDA Monitoring subsystem. A proxy manager is also run,
enabling certificate-based authentication and authorization.

### 2017-03-12 overall.tex
scattered changes.

Figure~\ref{fig:core-hours-utilization} shows the number of core hours used by
ATLAS on Titan, from January 2016 to February 2017. During that period, ATLAS
consumed a total of 73.8M core hours, for an average of 7M hours a month, with a
minimum of 3.3M hours in April 2016 and a maximum 14.8M hours in February 2017.

>>>>

Figure~\ref{fig:core-hours-utilization} shows the number of core hours used by
ATLAS on Titan, from January 2016 to February 2017. During that period, ATLAS
consumed a total of 73.8M core-hours, for an average of 7M core-hours a month, with a
minimum of 3.3M core-hours in April 2016 and a maximum 14.8M core-hours in February 2017.
